---
title: <span style="color:#d65cad"><font size="20">Bollywood  Films of 2015</font></span>
author: "Krishna Kuyate Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
font-family: 'Risque'
---

<span style="color:#800080"><font size="4">
We are almost at the end of year 2015 and it has been an interesting year for Bollywood movies and songs.
</span>

<span style="color:#800080">
It has been a year ofmixed movies: the usual light-hearted commercial ones to the hard content,serious movies to the absolutely heroine-oriented movies,each of them making a mark among the audience. 
</span>

<span style="color:#800080">
2015  has been a  good business  year for  Bollywood films as many of the  movies worked well  with the audience.However,it is surprising that most popular songs of 2015 are from movies that have not done well at the box office.
</font>
</span>

```{r include=FALSE}
library(magick)
image_read("Wallpaper.jpg")->img1
image_resize(img1, "800x800")->img1


```

```{r echo=FALSE}
image_oilpaint(img1,radius = 2)
```

```{r include=FALSE}
##@Import Package and data file
library(readr)
Bollywood_Movie_Data <- read_csv("Bollywood_Movie_Data.csv")
View(Bollywood_Movie_Data)
##Convert dataset into dataframe
Bollywood_Movie_Data_Df<-as.data.frame(Bollywood_Movie_Data)
##Find out the no. of variable in dataset:
paste("No. of variable in 'Bollywood_Movie_Data ' dataset :",ncol(Bollywood_Movie_Data_Df))

##Find out no. of Observation in dataset:
paste("No. of Observation in 'Bollywood_Movie_Data ' dataset :",nrow(Bollywood_Movie_Data_Df))
##Find out the no. of movies data present:
na.omit(Bollywood_Movie_Data_Df$Movie_Name)->Movie_List
paste("No. of movies data present 'Bollywood_Movie_Data ' dataset :",length(unique(Movie_List)))
##Structure of dataset:
str(Bollywood_Movie_Data_Df)

##Summary
summary(Bollywood_Movie_Data_Df)


```


<font size="5">"Arre wo Samba, Kitane Movies Release Huye.......!!!"</font>
```{r include=FALSE}
image_read("movie_count.jpg")->movie_count
image_resize(movie_count,"1500x500")->movie_count1

```

```{r echo=FALSE,fig.width=10,fig.height=4}
movie_count1

```

<font size="4">Total No. of Movies Release in 2015:</font>
```{r echo=FALSE}
length(unique(Movie_List))

```

<font size="5">"Tarikh pe Tarikh.....Tarikh pe Tarik..Her Tarike pe aa rhi  he ye Movie...."</font>
``````{r include=FALSE}
image_read("movie_tarikh.jpg")->movie_tarikh
image_resize(movie_tarikh,"1500x500")->movie_tarikh1

```

```{r echo=FALSE}
movie_tarikh1
```


```{r include=FALSE}
##No.Of Movie vs Month Analysis:
library(lubridate)
library(dplyr)
library(ggplot2)
#Bollywood_Movie_Data_Df$Release_date
month(Bollywood_Movie_Data_Df$Release_date,label = TRUE)->month_movie


#Bollywood_Movie_Data_Df$Movie_Name,month_movie
data.frame(Bollywood_Movie_Data_Df$Movie_Name,month_movie)->month_movie_df
month_movie_df%>%count(month_movie)->month_movie_dfc
colnames(month_movie_dfc)<-c("Month of Release","No. of Movie")
#Table:
month_movie_dfc
```


```{r echo=FALSE ,fig.width=10,fig.height=4}
#Graph:

ggplot(month_movie_dfc,aes(x=`Month of Release`,y=`No. of Movie`,fill=`Month of Release`))+geom_bar(stat = "identity",position="dodge")+ylab("Movies Released")+xlab("Month")+ggtitle("Movies Released:Monthwise Analysis")+theme(plot.title = element_text(face = "bold.italic",colour = "#800080",size =20))+geom_point()


```

```{r echo=FALSE,fig.width=10,fig.height=4}
month_movie_dfc
```


<font size="5">"Paisa ......Jab Bolta he ..."</font>

``````{r include=FALSE}
image_read("coll.jpg")->coll
image_resize(coll,"1500x500")->coll1

```

```{r echo=FALSE}
coll1
```


<font size="4">Total O Collection in 2015:</font>
```{r echo=FALSE}
#Total O collection
sum(Bollywood_Movie_Data_Df$Ocollection)->smo
paste(smo,"Million")
```


<font size="4">Total w Collection in 2015:</font>
```{r include=FALSE}
#Total W collection
na.omit(Bollywood_Movie_Data_Df$Wcollection)
sum(na.omit(Bollywood_Movie_Data_Df$Wcollection))->smw
paste0(smw,"Millions")
```

```{r echo=FALSE}
paste0(smw,"Millions")
```

<font size="4">Total F Collection in 2015:</font>

```{r include=FALSE}
#Total F collection
na.omit(Bollywood_Movie_Data_Df$Fwcollection)
sum(na.omit(Bollywood_Movie_Data_Df$Fwcollection))->smf

```
```{r echo=FALSE}
paste0(smf,"Millions")
```

<font size="4">Total T Collection in 2015:</font>
```{r include=FALSE}
#Total T collection
na.omit(Bollywood_Movie_Data_Df$Tcollection)
sum(na.omit(Bollywood_Movie_Data_Df$Tcollection))->smt


```

```{r echo=FALSE}
paste(smt,"Millions")
```

<font size="4">Top 5 Movie according to o collections:</font>

```{r include=FALSE}
#top 5 Movie according to o collections
Bollywood_Movie_Data_Df[order(Bollywood_Movie_Data_Df$Ocollection,decreasing = TRUE),]->ocdf
data.frame("Movie Name"=ocdf$Movie_Name,"O Collection"=ocdf$Ocollection)->ocdf5
ocdf5[1:5,]->ocdf6
as.data.frame(ocdf6)->ocdf6
#Table:
ocdf6
```

```{r echo=FALSE}
ocdf6
```


<font size="4">Top 5 Movie according to W collections:</font>
```{r include=FALSE}
#top 5 Movie according to w collections
Bollywood_Movie_Data_Df[order(Bollywood_Movie_Data_Df$Wcollection,decreasing = TRUE),]->wcdf
data.frame("Movie Name"=wcdf$Movie_Name,"w Collection"=wcdf$Wcollection)->wcdf5
#Table:
wcdf5[1:5,]->wcdf5
as.data.frame(wcdf5)->wcdf6

```

```{r echo=FALSE}
wcdf6
```

<font size="4">Top 5 Movie according to F collections:</font>
```{r include=FALSE}
#Top 5 Movies according to F collection:
Bollywood_Movie_Data_Df[order(Bollywood_Movie_Data_Df$Fwcollection,decreasing = TRUE),]->fcdf
data.frame("Movie Name"=fcdf$Movie_Name,"F Collection"=fcdf$Fwcollection)->fcdf5
#table:
fcdf5[1:5,]->fcdf6
as.data.frame(fcdf6)->fcdf6

```

```{r echo=FALSE}
fcdf6
```


<font size="4">Top 5 Movie according to T collections:</font>
```{r include=FALSE}
#Top 5 Movie accrding to T Collection :
Bollywood_Movie_Data_Df[order(Bollywood_Movie_Data_Df$Tcollection,decreasing = TRUE),]->tcdf
data.frame("Movie Name"=tcdf$Movie_Name,"T Collections"=tcdf$Tcollection)->tcdf5
#table:
tcdf5[1:5,]->tcdf6
as.data.frame(tcdf6)->tcdf6

```

```{r echo=FALSE}
tcdf6
```


<font size="4">Top 5 Movie and Collection Analysis:</font>
```{r include=FALSE}
########Graph:#####################
grid_col<-matrix(1:4 ,ncol = 4)
layout(grid_col)
#o collections
og<-ggplot(ocdf6,aes(x=ocdf6$Movie.Name,y=ocdf6$O.Collection,fill=Movie.Name))+geom_bar(stat = "identity",position="dodge")+ylab("O Collection")+xlab("Movie Name")+theme(axis.text.x = element_text(angle = 45, hjust = 1))+ ggtitle("Movie Name  vs O collections")

#W collection
wg<-ggplot(wcdf6,aes(x=wcdf6$Movie.Name,y=wcdf6$w.Collection,fill=Movie.Name))+geom_bar(stat = "identity",position="dodge")+ylab("W Collection")+xlab("Movie Name")+theme(axis.text.x = element_text(angle = 45, hjust = 1))+ ggtitle("Movie Name  vs W collections")

#F cOllection
fg<-ggplot(fcdf6,aes(x=fcdf6$Movie.Name,y=fcdf6$F.Collection,fill=Movie.Name))+geom_bar(stat = "identity",position="dodge")+ylab("F Collection")+xlab("Movie Name")+theme(axis.text.x = element_text(angle = 45, hjust = 1))+ ggtitle("Movie Name  vs F collections")

#T collection
tg<-ggplot(tcdf6,aes(x=tcdf6$Movie.Name,y=tcdf6$T.Collections,fill=Movie.Name))+geom_bar(stat = "identity",position="dodge")+ylab("T Collection")+xlab("Movie Name")+theme(axis.text.x = element_text(angle = 45, hjust = 1))+ ggtitle("Movie Name  vs T collections")


library(gridExtra)

grid.arrange(og,wg,fg,tg,ncol=2)


```


```{r echo=FALSE,fig.width=10,fig.height=8}
grid.arrange(og,wg,fg,tg,ncol=2)
```

<font size="5">"Mai Hu Tera Hero.................</font>
```{r include=FALSE}
image_read("actor.jpg")->actor_img
image_resize(actor_img,"1500x500")->actor_img1

```

```{r echo=FALSE}
actor_img1
```



<font size="4">Total No .of  actors work in 2015:</font>
```{r echo=FALSE}
na.omit(Bollywood_Movie_Data_Df$Acter_Name)->Actors
Actors_u<-unique(Actors)
length(Actors_u)

```


<font size="4">Actor name list</font>
```{r echo=FALSE}
Actors_u

```

<font size="4"> Actor and Movies Count</font>
```{r echo=FALSE}
##Actor  and Movies Count:
Bollywood_Movie_Data_Df%>%count(Bollywood_Movie_Data_Df$Acter_Name)->acto_mov_c
as.data.frame(acto_mov_c)->acto_mov_c
colnames(acto_mov_c)<-c("Actor Name","Total Movies")
#Table:
acto_mov_c
```


<font size="4"> Top Actor  according to movies count</font>
```{r echo=FALSE}
##Top Actor  according to movies count
acto_mov_c[order(acto_mov_c$`Total Movies`,decreasing = TRUE),]->acto_mov_c5
as.data.frame(acto_mov_c5)->acto_mov_c51
#Table:
acto_mov_c51[1,]
```


<font size="4"> Top 5 Actor accroding to movies count:</font>
```{r echo=FALSE, fig.width=10,fig.height=7}
#table:
acto_mov_c51[1:5,]
#Graph:
acto_mov_c51[1:5,]->acto_mov_c5_df
as.data.frame(acto_mov_c5_df)->acto_mov_c5_df
library(plotrix)
par(col.main="blue")
pie3D(acto_mov_c5_df$`Total Movies`,radius=0.8,height=0.1,theta=pi/3,main="Top 5 Actor  Movies Analysis:",labels=acto_mov_c5_df$`Total Movies`,explode=0.2,shade=0.6)
legend("topright",legend=acto_mov_c5_df$`Actor Name`,fill=acto_mov_c5_df$`Total Movies`,cex = 0.8)

```



<font size="4"> Top 5 Actor and collections</font>
```{r include=FALSE}
acto_coll_df<-data.frame(Actor_cl=Bollywood_Movie_Data_Df$Acter_Name,
           O_Collection_a=Bollywood_Movie_Data_Df$Ocollection,
           w_Collection_a=Bollywood_Movie_Data_Df$Wcollection,
           F_Collection_a=Bollywood_Movie_Data_Df$Fwcollection,
           T_Collection_a=Bollywood_Movie_Data_Df$Tcollection)


#Table Function :
Top_act_for_collection_t<-function(Collection_type,agg_by)
{
  
  aggregate(Collection_type,by=list(agg_by),FUN=sum)->aff_col_df
  as.data.frame(aff_col_df)->aff_col_df
  aff_col_df[order(aff_col_df$x,decreasing = TRUE),]->aff_col_df5
  aff_col_df5[1:5,]->aff_col_df5_t
  as.data.frame(aff_col_df5_t)->aff_col_df5_tdf
  colnames(aff_col_df5_tdf)<-c("Actor","Total Collection 2015")
  #Table:
  aff_col_df5_tdf
  
}


#Graph Function :
Top_act_for_collection_g<-function(Collection_type,agg_by,title,yaxix)
{
  
  aggregate(Collection_type,by=list(agg_by),FUN=sum)->aff_col_df
  as.data.frame(aff_col_df)->aff_col_df
  aff_col_df[order(aff_col_df$x,decreasing = TRUE),]->aff_col_df5
  aff_col_df5[1:5,]->aff_col_df5_t
  as.data.frame(aff_col_df5_t)->aff_col_df5_tdf
  colnames(aff_col_df5_tdf)<-c("Actor","Total Collection 2015")
  #Table:
  aff_col_df5_tdf
  #Graph:
  
  graph_ti=title
  yaxis_g=yaxix
  ggplot(aff_col_df5_tdf,aes(x=Actor,y=`Total Collection 2015`,fill=Actor))+ geom_bar(stat = "identity",position="dodge")+ggtitle(graph_ti)+theme(plot.title = element_text(face = "bold.italic"))+xlab("Actor Name")+ylab(yaxis_g)+theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
}


```



<font size="4"> Top 5 Actor and o collections:  </font>

<font size="4">Table:</font>
```{r echo=FALSE}
Top_act_for_collection_t(acto_coll_df$O_Collection_a,acto_coll_df$Actor_cl)
```

<font size="4"> Graph:</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_g(acto_coll_df$O_Collection_a,acto_coll_df$Actor_cl,"Actor Name Vs O Collection","O Collection")
```


<font size="4"> Top 5 Actor and F collections: </font>

<font size="4">Table:</font>
```{r echo=FALSE}
Top_act_for_collection_t(acto_coll_df$F_Collection_a,acto_coll_df$Actor_cl)
```
<font size="4"> Graph:</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_g(acto_coll_df$F_Collection_a,acto_coll_df$Actor_cl,"Actor Name Vs F Collection","F Collection")
```

<font size="4"> Top 5 Actor and W collections: </font>

<font size="4">Table:</font>
```{r echo=FALSE}
Top_act_for_collection_t(acto_coll_df$w_Collection_a,acto_coll_df$Actor_cl)
```
<font size="4"> Graph:</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_g(acto_coll_df$F_Collection_a,acto_coll_df$Actor_cl,"Actor Name Vs W Collection","W Collection")
```

<font size="4"> Top 5 Actor and T collections: </font>

<font size="4">Table:</font>
```{r echo=FALSE}
Top_act_for_collection_t(acto_coll_df$T_Collection_a,acto_coll_df$Actor_cl)
```
<font size="4"> Graph:</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_g(acto_coll_df$T_Collection_a,acto_coll_df$Actor_cl,"Actor Name Vs T Collection","T Collection")

```

<font size="5">"Success......Movie.....Money...."</font>

```{r include=FALSE}
image_read("verdict.jpg")->verdict_img
verdict_img1<-image_resize(verdict_img,"1500x500")
Bollywood_Movie_Data_Df%>%count(Bollywood_Movie_Data_Df$Verdict)->ver_df

as.data.frame(ver_df)->ver_df
colnames(ver_df)<-c("Movie Status","Total Count")
#Graph:

library(ggvis)
```

```{r echo=FALSE}
verdict_img1

```

```{r echo=FALSE ,fig.width=10,fig.height=4}


ver_df


ver_df %>% ggvis(~`Movie Status`, ~`Total Count`,fill:="Blue", size := 600, opacity := 0.4) %>% layer_points()%>% add_axis("x",title = "Movie Success Status", title_offset = 50)%>%add_axis("y",title = "Total Movie Count", title_offset = 50)

```




























