---
title: <span style="color:black"><font size="20">Bollywood  Blokblaster</font></span>
author: "Krishna Kuyate Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
font-family: 'Risque'
theme: architect
keep_md: true

---

<body background="bk.jpg">



```{r include=FALSE}
library(magick)
library(knitr)
library(kableExtra)
image_read("start.jpg")->img1_s
image_resize(img1_s, "800x800")->img1_s1

```
```{r echo=FALSE,fig.width=10,fig.height=5,fig.fullwidth=TRUE}
img1_s1
```

<p align="justify"><font size="4">
We are almost at the end of year 2015 and it has been an interesting year for Bollywood movies and songs.It has been a year ofmixed movies: the usual light-hearted commercial ones to the hard content,serious movies to the absolutely heroine-oriented movies,each of them making a mark among the audience. 2015  has been a  good business  year for  Bollywood films as many of the  movies worked well  with the audience.However,it is surprising that most popular songs of 2015 are from movies that have not done well at the box office.
</font>
</p>

```{r include=FALSE}

image_read("Wallpaper.jpg")->img1
image_resize(img1, "800x800")->img1


```

```{r echo=FALSE ,fig.width=10,fig.height=5}
image_oilpaint(img1,radius = 2)
```

```{r include=FALSE}
##@Import Package and data file
library(readr)
Bollywood_Movie_Data <- read_csv("Bollywood_Movie_Data.csv")
View(Bollywood_Movie_Data)
##Convert dataset into dataframe
Bollywood_Movie_Data_Df<-as.data.frame(Bollywood_Movie_Data)
##Find out the no. of variable in dataset:
paste("No. of variable in 'Bollywood_Movie_Data ' dataset :",ncol(Bollywood_Movie_Data_Df))

##Find out no. of Observation in dataset:
paste("No. of Observation in 'Bollywood_Movie_Data ' dataset :",nrow(Bollywood_Movie_Data_Df))
##Find out the no. of movies data present:
na.omit(Bollywood_Movie_Data_Df$Movie_Name)->Movie_List
paste("No. of movies data present 'Bollywood_Movie_Data ' dataset :",length(unique(Movie_List)))
##Structure of dataset:
str(Bollywood_Movie_Data_Df)

##Summary
summary(Bollywood_Movie_Data_Df)


```
<br>
<br>

<font size="7">"Arre wo Samba, Kitane Movies Release Huye.......!!!"</font>

<p align="justify"><font size="4">Bollywood Movies 2015 with release dates  calendar for all New Hindi Movies. The list for all the major movies is tentative and  may get changed due to various reasons by producers.<font></P>
```{r include=FALSE}
image_read("movie_count.jpg")->movie_count
image_resize(movie_count,"1500x500")->movie_count1

```

```{r echo=FALSE,fig.width=10,fig.height=5}
movie_count1

```

<font size="4">**Total No. of Movies Release in 2015:**</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
length(unique(Movie_List))

```
<br>
<br>
<font size="7">"Tarikh pe Tarikh.....Tarikh pe Tarik..Her Tarike pe aa rhi  he ye Movie...."</font>
<p align="justify"><font size="4">The world's movie capital is not Hollywood but Bollywood. Bollywood is the nickname for the Indian film industry located in Bombay (now known as Mumbai, though Mollywood hasn't quite caught on.)</font></p>

``````{r include=FALSE}
image_read("movie_tarikh.jpg")->movie_tarikh
image_resize(movie_tarikh,"1500x500")->movie_tarikh1

```

```{r echo=FALSE,fig.width=10,fig.height=5}
movie_tarikh1
```


```{r include=FALSE}
##No.Of Movie vs Month Analysis:
library(lubridate)
library(dplyr)
library(ggplot2)
#Bollywood_Movie_Data_Df$Release_date
month(Bollywood_Movie_Data_Df$Release_date,label = TRUE)->month_movie


#Bollywood_Movie_Data_Df$Movie_Name,month_movie
data.frame(Bollywood_Movie_Data_Df$Movie_Name,month_movie)->month_movie_df
month_movie_df%>%count(month_movie)->month_movie_dfc
colnames(month_movie_dfc)<-c("Month of Release","No. of Movie")
#Table:
month_movie_dfc
```


```{r echo=FALSE ,fig.width=10,fig.height=5}
#Graph:

ggplot(month_movie_dfc,aes(x=`Month of Release`,y=`No. of Movie`,fill=`Month of Release`))+geom_bar(stat = "identity",position="dodge")+ylab("Movies Released")+xlab("Month")+ggtitle("Movies Released:Monthwise Analysis")+theme(plot.title = element_text(face = "bold.italic",colour = "#800080",size =20))+geom_point()


```

```{r echo=FALSE,fig.width=10,fig.height=5}
kable(month_movie_dfc,format = "html",booktabs=TRUE,caption ="Movies Released:Monthwise Analysis",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```
<br>
<br>

<font size="7">"Paisa ......Jab Bolta he ..."</font>
<p align="justify"><font size="4">Indians are in love with movies, even though most films follow a similar format called masala (the word for a collection of spices). Movies are three to four hours long (and include an intermission), include dozens of songs and dances (featuring 100 or so choreographed dancers), top stars, the story between the songs of boy meets girl (without any kissing or sexual contact), lots of action (though no bloodshed), and always - a happy ending.</font></p>

``````{r include=FALSE}
image_read("coll.jpg")->coll
image_resize(coll,"1500x500")->coll1

```

```{r echo=FALSE ,fig.width=10,fig.height=5}
coll1
```
<br>
<p align="justify"><font size="4">Truly the Gods are shining down on Indian stars as never before and Bollywood’s stars are shining brighter than ever.</font></p>

<font size="4">**Total O Collection in 2015:**</font>
```{r echo=FALSE ,fig.width=10,fig.height=5}
#Total O collection
sum(Bollywood_Movie_Data_Df$Ocollection)->smo
paste(smo,"Million")
```


<font size="4">**Total w Collection in 2015:**</font>
```{r include=FALSE}
#Total W collection
na.omit(Bollywood_Movie_Data_Df$Wcollection)
sum(na.omit(Bollywood_Movie_Data_Df$Wcollection))->smw
paste0(smw,"Millions")
```

```{r echo=FALSE ,fig.width=10,fig.height=5}
paste0(smw,"Millions")
```

<font size="4">**Total F Collection in 2015:**</font>

```{r include=FALSE}
#Total F collection
na.omit(Bollywood_Movie_Data_Df$Fwcollection)
sum(na.omit(Bollywood_Movie_Data_Df$Fwcollection))->smf

```
```{r echo=FALSE ,fig.width=10,fig.height=5}
paste0(smf,"Millions")
```

<font size="4">**Total T Collection in 2015:**</font>
```{r include=FALSE}
#Total T collection
na.omit(Bollywood_Movie_Data_Df$Tcollection)
sum(na.omit(Bollywood_Movie_Data_Df$Tcollection))->smt


```

```{r echo=FALSE,fig.width=10,fig.height=5}
paste(smt,"Millions")
```



```{r include=FALSE}
#top 5 Movie according to o collections
Bollywood_Movie_Data_Df[order(Bollywood_Movie_Data_Df$Ocollection,decreasing = TRUE),]->ocdf
data.frame("Movie Name"=ocdf$Movie_Name,"O Collection"=ocdf$Ocollection)->ocdf5
ocdf5[1:5,]->ocdf6
as.data.frame(ocdf6)->ocdf6
#Table:
ocdf6
```

```{r echo=FALSE,fig.width=10,fig.height=5}

kable(ocdf6,format = "html",booktabs=TRUE,caption ="Top 5 Movie according to o collections",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```



```{r include=FALSE}
#top 5 Movie according to w collections
Bollywood_Movie_Data_Df[order(Bollywood_Movie_Data_Df$Wcollection,decreasing = TRUE),]->wcdf
data.frame("Movie Name"=wcdf$Movie_Name,"w Collection"=wcdf$Wcollection)->wcdf5
#Table:
wcdf5[1:5,]->wcdf5
as.data.frame(wcdf5)->wcdf6

```

```{r echo=FALSE,fig.width=10,fig.height=5}
kable(wcdf6,format = "html",booktabs=TRUE,caption ="Top 5 Movie according to w collections",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```


```{r include=FALSE}
#Top 5 Movies according to F collection:
Bollywood_Movie_Data_Df[order(Bollywood_Movie_Data_Df$Fwcollection,decreasing = TRUE),]->fcdf
data.frame("Movie Name"=fcdf$Movie_Name,"F Collection"=fcdf$Fwcollection)->fcdf5
#table:
fcdf5[1:5,]->fcdf6
as.data.frame(fcdf6)->fcdf6

```

```{r echo=FALSE,fig.width=10,fig.height=5}
kable(fcdf6,format = "html",booktabs=TRUE,caption ="Top 5 Movie according to F collections",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```



```{r include=FALSE}
#Top 5 Movie accrding to T Collection :
Bollywood_Movie_Data_Df[order(Bollywood_Movie_Data_Df$Tcollection,decreasing = TRUE),]->tcdf
data.frame("Movie Name"=tcdf$Movie_Name,"T Collections"=tcdf$Tcollection)->tcdf5
#table:
tcdf5[1:5,]->tcdf6
as.data.frame(tcdf6)->tcdf6

```

```{r echo=FALSE,fig.width=10,fig.height=5}
kable(tcdf6,format = "html",booktabs=TRUE,caption ="Top 5 Movie according to T collections",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```


<font size="4">**Top 5 Movie and Collection Analysis:**</font>
<br>
<p align="justify"><font size="4">Yes! There is no disputing that finally Bollywood has arrived and its stars are shining bright. It doesn’t matter which part of the globe you live in anymore.</font></p>
```{r include=FALSE}
########Graph:#####################
grid_col<-matrix(1:4 ,ncol = 4)
layout(grid_col)
#o collections
og<-ggplot(ocdf6,aes(x=ocdf6$Movie.Name,y=ocdf6$O.Collection,fill=Movie.Name))+geom_bar(stat = "identity",position="dodge")+ylab("O Collection")+xlab("Movie Name")+theme(axis.text.x = element_text(angle = 45, hjust = 1))+ ggtitle("Movie Name  vs O collections")

#W collection
wg<-ggplot(wcdf6,aes(x=wcdf6$Movie.Name,y=wcdf6$w.Collection,fill=Movie.Name))+geom_bar(stat = "identity",position="dodge")+ylab("W Collection")+xlab("Movie Name")+theme(axis.text.x = element_text(angle = 45, hjust = 1))+ ggtitle("Movie Name  vs W collections")

#F cOllection
fg<-ggplot(fcdf6,aes(x=fcdf6$Movie.Name,y=fcdf6$F.Collection,fill=Movie.Name))+geom_bar(stat = "identity",position="dodge")+ylab("F Collection")+xlab("Movie Name")+theme(axis.text.x = element_text(angle = 45, hjust = 1))+ ggtitle("Movie Name  vs F collections")

#T collection
tg<-ggplot(tcdf6,aes(x=tcdf6$Movie.Name,y=tcdf6$T.Collections,fill=Movie.Name))+geom_bar(stat = "identity",position="dodge")+ylab("T Collection")+xlab("Movie Name")+theme(axis.text.x = element_text(angle = 45, hjust = 1))+ ggtitle("Movie Name  vs T collections")


library(gridExtra)

grid.arrange(og,wg,fg,tg,ncol=2)


```


```{r echo=FALSE,fig.width=10,fig.height=8}
grid.arrange(og,wg,fg,tg,ncol=2)
```

<br>
<br>
<font size="7">"Mai Hu Tera Hero.................</font>
<p align="justify"><font size="4">The stars of Bollywood are very popular and highly paid, considering the budget of the films. The lead star in a film often receives as much as 40% of the US $2 million budget for the typical masala film. Stars may be in such high demand that they're working on ten films at once. Photographs of Bollywood stars grace shop windows and homes throughout the country.</font></p>
```{r include=FALSE}
image_read("actor.jpg")->actor_img
image_resize(actor_img,"1500x500")->actor_img1

```

```{r echo=FALSE,fig.width=10,fig.height=5}
actor_img1
```



<font size="4">**Total No .of  actors work in 2015:**</font>

```{r echo=FALSE,fig.width=10,fig.height=5}
na.omit(Bollywood_Movie_Data_Df$Acter_Name)->Actors
Actors_u<-unique(Actors)
length(Actors_u)

```

<br>
<font size="4">**Actor name list:**</font>

<p align="justify"><font size="4">As years have gone by, Bollywood actually has begun to have a major influence on Western culture now. The Bollywood film industry has been around for tens and hundreds of years. Even though its not as well known as it should be, it has a big impact in film and music industry through out the world. </font></p>
```{r echo=FALSE,fig.width=10,fig.height=5}

kable(Actors_u,format = "html",booktabs=TRUE,caption ="Actor List",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1,width = "36em",background = "#ddccff")%>%scroll_box(height = "500px")

```

<br>
<font size="4"> **Actor and Movies Count**</font>

<p align="justify"><font size="4">It is a form of art with the ability to entertain, educate, and reflect and shape our sense of who we are and our understanding of the society in which we live in. In Hindi films there exits the hero and heroine, however gender hierarchy can be seen and importance is imposed on the male actor. One would agree that the Hindi film industry is male-centric, with limited space for females to be versatile in the character they play.</font></p>
```{r echo=FALSE,fig.width=10,fig.height=5}
##Actor  and Movies Count:
Bollywood_Movie_Data_Df%>%count(Bollywood_Movie_Data_Df$Acter_Name)->acto_mov_c
as.data.frame(acto_mov_c)->acto_mov_c
colnames(acto_mov_c)<-c("Actor Name","Total Movies")
#Table:

kable(acto_mov_c,format = "html",booktabs=TRUE,caption ="Actor and Movies Count",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")%>%scroll_box(height = "500px")
```


<font size="4"> **Top Actor  according to movies count**</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
##Top Actor  according to movies count
acto_mov_c[order(acto_mov_c$`Total Movies`,decreasing = TRUE),]->acto_mov_c5
as.data.frame(acto_mov_c5)->acto_mov_c51
#Table:
kable(acto_mov_c51[1,],format = "html",booktabs=TRUE,caption ="Top Actor According to Movie Count",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```
<br>

<font size="4"> **Top 5 Actor accroding to movies count:**</font>
<p align="justify"><font size="4">The actor or actress has the ability to perform a particular character and not just perform but literally living the character for the particular role given to him. </font></p>
```{r echo=FALSE, fig.width=10,fig.height=7}
#table:

kable(acto_mov_c51[1:5,],format = "html",booktabs=TRUE,caption ="Top 5 Actor Accroding to movie count",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
#Graph:
acto_mov_c51[1:5,]->acto_mov_c5_df
as.data.frame(acto_mov_c5_df)->acto_mov_c5_df
library(plotrix)
par(col.main="blue")
pie3D(acto_mov_c5_df$`Total Movies`,radius=0.8,height=0.1,theta=pi/3,main="Top 5 Actor  Movies Analysis:",labels=acto_mov_c5_df$`Total Movies`,explode=0.2,shade=0.6)
legend("topright",legend=acto_mov_c5_df$`Actor Name`,fill=acto_mov_c5_df$`Total Movies`,cex = 0.8)

```



<font size="4"> **Top 5 Actor and collections**</font>
<p align="justify"><font size="4">Acting has so much to do with stories, emotions, drama, expressions, music and timing. An actor justifies his character on the screen or live and gets appreciated. Acting can only be done if the role has you as a part of it. If you do not involve and indulge into what the role demands then you will not be liked by the audience. </font></p>
```{r include=FALSE}
acto_coll_df<-data.frame(Actor_cl=Bollywood_Movie_Data_Df$Acter_Name,
           O_Collection_a=Bollywood_Movie_Data_Df$Ocollection,
           w_Collection_a=Bollywood_Movie_Data_Df$Wcollection,
           F_Collection_a=Bollywood_Movie_Data_Df$Fwcollection,
           T_Collection_a=Bollywood_Movie_Data_Df$Tcollection)


#Table Function :
Top_act_for_collection_t<-function(Collection_type,agg_by)
{
  
  aggregate(Collection_type,by=list(agg_by),FUN=sum)->aff_col_df
  as.data.frame(aff_col_df)->aff_col_df
  aff_col_df[order(aff_col_df$x,decreasing = TRUE),]->aff_col_df5
  aff_col_df5[1:5,]->aff_col_df5_t
  as.data.frame(aff_col_df5_t)->aff_col_df5_tdf
  colnames(aff_col_df5_tdf)<-c("Actor","Total Collection 2015")
  #Table:
  aff_col_df5_tdf
  
}


#Graph Function :
Top_act_for_collection_g<-function(Collection_type,agg_by,title,yaxix)
{
  
  aggregate(Collection_type,by=list(agg_by),FUN=sum)->aff_col_df
  as.data.frame(aff_col_df)->aff_col_df
  aff_col_df[order(aff_col_df$x,decreasing = TRUE),]->aff_col_df5
  aff_col_df5[1:5,]->aff_col_df5_t
  as.data.frame(aff_col_df5_t)->aff_col_df5_tdf
  colnames(aff_col_df5_tdf)<-c("Actor","Total Collection 2015")
  #Table:
  aff_col_df5_tdf
  #Graph:
  
  graph_ti=title
  yaxis_g=yaxix
  ggplot(aff_col_df5_tdf,aes(x=Actor,y=`Total Collection 2015`,fill=Actor))+ geom_bar(stat = "identity",position="dodge")+ggtitle(graph_ti)+theme(plot.title = element_text(face = "bold.italic"))+xlab("Actor Name")+ylab(yaxis_g)+theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
}


```



<font size="4"> **Top 5 Actor and o collections: ** </font>

<font size="4">*Table:*</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_t(acto_coll_df$O_Collection_a,acto_coll_df$Actor_cl)->otp
kable(otp,format = "html",booktabs=TRUE,caption ="Top 5 Actor and o collections",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```

<font size="4"> *Graph:*</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_g(acto_coll_df$O_Collection_a,acto_coll_df$Actor_cl,"Actor Name Vs O Collection","O Collection")
```


<font size="4"> **Top 5 Actor and F collections:** </font>

<font size="4">*Table:*</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_t(acto_coll_df$F_Collection_a,acto_coll_df$Actor_cl)->ftp
kable(ftp,format = "html",booktabs=TRUE,caption ="Top 5 Actor and F collections",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```
<font size="4"> *Graph:*</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_g(acto_coll_df$F_Collection_a,acto_coll_df$Actor_cl,"Actor Name Vs F Collection","F Collection")
```

<font size="4"> **Top 5 Actor and W collections:** </font>

<font size="4">*Table:*</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_t(acto_coll_df$w_Collection_a,acto_coll_df$Actor_cl)->wtp
kable(wtp,format = "html",booktabs=TRUE,caption ="Top 5 Actor and W collections",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```
<font size="4"> *Graph:*</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_g(acto_coll_df$F_Collection_a,acto_coll_df$Actor_cl,"Actor Name Vs W Collection","W Collection")
```

<font size="4"> **Top 5 Actor and T collections: **</font>

<font size="4">*Table:*</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_t(acto_coll_df$T_Collection_a,acto_coll_df$Actor_cl)->ttp
kable(ttp,format = "html",booktabs=TRUE,caption ="Top 5 Actor and T collections",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")
```
<font size="4"> *Graph:*</font>
```{r echo=FALSE,fig.width=10,fig.height=5}
Top_act_for_collection_g(acto_coll_df$T_Collection_a,acto_coll_df$Actor_cl,"Actor Name Vs T Collection","T Collection")

```

<font size="7">"Success......Movie.....Money...."</font>

<p align="justify"><font size="4">Bollywood movies and their stars are gaining grounds everywhere. All over the world America, Europe, Australia, the Persian Gulf and other parts of Asia as well Bollywood movies are being watched and Bollywood stars are creating the kind of madness associated with only Hollywood stars before.</font></p>

```{r include=FALSE}
image_read("verdict.jpg")->verdict_img
verdict_img1<-image_resize(verdict_img,"1500x500")
Bollywood_Movie_Data_Df%>%count(Bollywood_Movie_Data_Df$Verdict)->ver_df

as.data.frame(ver_df)->ver_df
colnames(ver_df)<-c("Movie Status","Total Count")
#Graph:

library(ggvis)
```

```{r echo=FALSE,fig.width=10,fig.height=5}
verdict_img1

```

```{r echo=FALSE ,fig.width=9,fig.height=5}


kable(ver_df,format = "html",booktabs=TRUE,caption ="Movie Success Status",align = 'c')%>%kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),full_width = F,position = "left")%>%column_spec(1:2,width = "30em",background = "#ddccff")


ver_df %>% ggvis(~`Movie Status`, ~`Total Count`,fill:="Blue", size := 600, opacity := 0.4) %>% layer_points()%>% add_axis("x",title = "Movie Success Status", title_offset = 50)%>%add_axis("y",title = "Total Movie Count", title_offset = 50)

```






```{r include=FALSE}
library(magick)
image_read("end.jpg")->img1_send
image_resize(img1_send, "800x800")->img1_s1end

```
```{r echo=FALSE}
img1_s1end
```







</body>














